Generating Simulated Data

### 2021-04-07 docs/SimData.Rmd
start binwidth automation

*Consider a function to do this using species max size, the vonB k and the desired number of bins for more consistency and to easily change Nsizebins.*
```{r lbinfunction, eval=FALSE}
# see e.g., https://www.sciencedirect.com/science/article/abs/pii/S0165783619303297
# estimated optimal bin size for VBGF estimation is 0.23 x Lmax ^0.6

@@

# need 2-par maturity curve based on length, atlantis maturity ogive based on age group

@@

>>>>

@@

The first pass through with the current bins results in very few lengths in the smallest bin for most species. This suggests we need to change the binwidths and possibly the number of bins to optimize length fitting. Perhaps a larger first bin or don't start it at 0?

*Consider a function to do this using species max size, the vonB k and the desired number of bins for more consistency and to easily change Nsizebins.* Do we need t0 as well? Haven't saved it.

```{r lbinfunction, eval=FALSE}
# see e.g., https://www.sciencedirect.com/science/article/abs/pii/S0165783619303297
# estimated optimal bin size for VBGF estimation is 0.23 x Lmax ^0.6

# see Ogle citing Schnute and Fornier on K as a growth increment
# https://derekogle.com/NCNRS349/modules/Growth/BKG
# K exponential rate of approach to asymptotic size
# exp(-K) fraction by which growth increment is multiplied each year
# at what length is increment*exp(-K) small? group those lengths into bigger bins

# pull observed min and max size from data to optimize start and end bins
minmaxlen <- list()
for(s in names(len_comp_data)){
  minmaxlen[[s]] <- len_comp_data[[s]][[1]] %>%
    dplyr::group_by(species) %>%
    dplyr::summarise(minlen = min(lower.bins, na.rm = TRUE),
                     maxlen = max(upper.bins, na.rm = TRUE)) 
}

# note!
# Green_halibut and Saithe have maxlen at 200 in at least one survey, 
# may need higher maxlength when running atlantisom comps wrapper, fix survey config files

@@

# need 2-par maturity curve based on length, atlantis maturity ogive based on age group
# or just translate age at 50% maturity to length and call it good?
